Microlensing as a possible probe of the internal structure of quasars

### 2015-07-12 paper1/theory.tex
figure2 with arrow
editing
improved figures 2-10

\begin{figure}
\includegraphics[width = .49\textwidth]{plots/infinite_fold.eps}
\caption{\label{fig:infinite_fold} Source profiles for Gaussian, disk,
  crescents (right) and magnification map for an infinite fold
  (left). Objects have the same $S_{0}$ and $r_{1/2}$. }
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{plots/4source_profile.eps}
	\includegraphics[width = 0.48\textwidth]{plots/4source_magnification.eps}
\caption{\label{fig:lightcurve_gauss} Lightcurves of crescents, gaussian and disk for sources with identical $S_0$ and $r_{1/2}$. Crescent source has $r_{1/2}$ = 0.72754 $R_p$, $R_n$ = 0.4 $R_p$, a = 0.3/-0.3 $R_p$ }
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{plots/4avar_profile.eps}
	\includegraphics[width = 0.48\textwidth]{plots/4avar_magnification.eps}
\caption{\label{fig:lightcurve_disk} Lightcurves of crescent sources with $R_n$ = 0.4 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{plots/4rn_profile.eps}
	\includegraphics[width = 0.48\textwidth]{plots/4rn_magnification.eps}
\caption{\label{fig:lightcurve_crescent_back} Lightcurves of backwards crescents with  a = 0.3 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{plots/4rn2_profile.eps}
	\includegraphics[width = 0.48\textwidth]{plots/4rn2_magnification.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurve of forwards crescents with a = -0.3 $R_p$.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width = .49\textwidth]{plots/infinite_fold_ar.eps}
\caption{\label{fig:infinite_fold} Source profiles for Gaussian, disk,
  crescents (right) and magnification map for an infinite fold
  (left). Objects have the same $S_{0}$ and $r_{1/2}$. The black arrow marks the direction of motion of the
sources relative to the caustic.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{plots/S1D_all.eps}
	\includegraphics[width = 0.48\textwidth]{plots/4source_magnification.eps}
\caption{\label{fig:lightcurve_gauss} Lightcurves of crescents, Gaussian and disk for sources with identical $S_0$ and $r_{1/2}$. Crescent source has $r_{1/2}$ = 0.72754 $R_p$, $R_n$ = 0.4 $R_p$, a = 0.3/-0.3 $R_p$ }
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{plots/S1D_var_a.eps}
	\includegraphics[width = 0.48\textwidth]{plots/4avar_magnification.eps}
\caption{\label{fig:lightcurve_disk} Lightcurves of crescent sources with $R_n$ = 0.4 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{plots/S1D_var_rn_a_poz.eps}
	\includegraphics[width = 0.48\textwidth]{plots/5Rn_back_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent_back} Lightcurves of backwards crescents with  a = 0.3 $R_p$.}
\end{figure}

@@

\begin{figure}
\centering
	\includegraphics[width = 0.48\textwidth]{plots/S1D_var_rn_a_neg.eps}
	\includegraphics[width = 0.48\textwidth]{plots/5Rn_forw_var_magnification.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurve of forwards crescents with a = -0.3 $R_p$.}
\end{figure}
